---
title: "R Notebook"
output:
  pdf_document:
    toc: yes
  html_document:
    fig_caption: yes
    keep_md: yes
    number_sections: yes
    toc: yes
editor_options:
  chunk_output_type: console
---

```{r setup_aer3, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,cache=TRUE,message=FALSE,warning=FALSE)

library("papaja")
library(ggplot2)
library(lemon)
library(Matrix)
library(ggmosaic)

library(knitr)
library(afex)
options(contrasts=c('contr.sum', 'contr.poly'))
afex_options(check_contrasts=FALSE, method_mixed="S")

library(data.table)
library(lme4)
library(lmerTest)
library(tidyverse)
library(emmeans)


# load exp2 data

#d2 <- readr::read_delim("../modPD2/modPD2_d2.csv", ",", escape_double = FALSE, trim_ws = TRUE)
load(file="./data/modPD2_d2.RData")

d2$RK_G <- d2$rkg
d2$RK_G[d2$RKG!="G"] <- "RK"
d2$RK_G <- factor(d2$RK_G, levels=c("G","RK"), ordered = TRUE)
d2$Confidence_ <- as.numeric(d2$Confidence)
d2$Confidence_[d2$Confidence!="low"] <- 4
d2$Confidence_ <- factor(d2$Confidence_, levels=c(1,4), labels=c("low", "med/high"), ordered = TRUE)

## Exclude participants who failed the PD training test
d2 <- subset(d2, include==TRUE)
d2p <- subset(d2, US_Valence!="none")

d2u <- subset(d2, US_Valence=="none")
d2ux <- subset(d2u, Instruction!="Exclusion")


### print an F test from mixed
print_mixedF <- function(obj, term){
  if (!any(row.names(obj$anova_table)==term)) term <- paste0("`",term,"`")
  index <- which(row.names(obj$anova_table)==term)
  outF <- paste0("$F(", obj$anova_table[index,1], ",", round(obj$anova_table[index,2], 2), ")=", round(obj$anova_table[index,3],2))
  outp <- printp(obj$anova_table[index,4])
  out <- paste0(outF, ", p", ifelse(str_sub(outp,1,1)=="<", "", "="), outp, "$")
}


```


## Evaluations and memory judgments of unpaired stimuli

In this section we focus on CS stimuli that were never paired with a US during the experiment.
As there are no experimental effects of US pairings, other influences on---or relations between---evaluations and memory may be more readily discerned in these (initially valent but) unpaired stimuli.
<!-- Any effects on their evaluations must be due to other influences such as regression to the mean or effects of pre-experimental valence.  -->
From one perspective, relations between memory and evaluations are due to biases that mask the existence of two independent representations, for instance when participants use their (pre-study) CS evaluations to inform memory responses by way of a heuristic used under uncertainty [an attitude-as-information heuristic, "I like it, so it must have been paired with positive USs"; @stahl_respective_2009; @hutter_dissociating_2012; @pleyers_aware_2007].
From another perspective; the relation between memory and evaluations arises because both judgments are based on the same single representation, [e.g., evaluations and valence-memory judgments are computed as summary evaluations of all previous encounters with the CS; @aust_memory-based_2018; @stahl_evaluative_2018].

### False-memory effects on evaluations

We first explored the hypothesis, discussed in the previous section, that the inverted EC effect for incorrect valence-memory responses is driven by high-confidence false memories.
For paired CSs, US valence memory accuracy predicted EC especially for high levels of confidence:
Those CSs believed to have been paired with pleasant USs were evaluated more pleasantly than CSs believed as having been paired with unpleasant USs; and this effect increased with increasing confidence in valence-memory responses.
This suggests that participants relied on their *perceived US valence* to evaluate the CSs.
Applied to nonpaired stimuli, this should result in a similar relation between US valence memory responses and pre-post evaluative change that is moderated by subjective confidence.
We computed linear mixed models for nonpaired CS stimuli with the Material and PD Instruction factors (as well as their interaction) as fixed effects in the baseline model, and with item and person random intercepts as well as random person slopes for CS Valence.
^[Thus, compared to the previous sections, we dropped the US Valence factor that has only a single level for nonpaired CSs. We again excluded Exclusion data because of potential carry-over effects.
The predictors of interest were added as covariates (i.e., without entering interactions with the Material and PD Instruction factors).]



```{r u2b, fig.cap="Pre-post evaluative changes (i.e., positive values indicate shift towards pleasant ratings) are linked with valence-memory responses; the link is moderated by confidence. Confidence data collapsed, for illustration, across the (relatively rare) medium- and high-confidence responses."}

par(mfrow=c(1,2))

u_ec_m_eq6 <- afex::mixed(data=d2ux, ec~Material*Instruction + CS_Valence + Confidence + CS_Valence:Confidence + vmval + vmval:Confidence + (1|cs) + (CS_Valence|id), method="S", progress=FALSE)
pq8 <- print_mixedF(u_ec_m_eq6, "vmval")
pq9 <- print_mixedF(u_ec_m_eq6, "Confidence:vmval")


# Confidence: interacts with vmval
# Note: we combined highest 2 levels because they have few cases

d2ux$`Valence memory response` <-  d2ux$vmval
d2ux$`Evaluative change` <- d2ux$ec
d2ux$`Confidence` <- d2ux$Confidence_
apa_lineplot(data=d2ux, id="cs", dv="Evaluative change", factors=c("Confidence","Valence memory response"), intercept=0, use = "all.obs", ylim=c(-4,4), args_title=list(sub="Confidence"))
u2_ec_c <- afex::mixed(data=d2ux, ec~Material*Instruction*CS_Valence + Confidence_*vmval + (1|cs) + (CS_Valence|id), method="S", progress=FALSE)
p_c <- print_mixedF(u2_ec_c, "Confidence_:vmval")

## PD Response: interacts with vmval

d2ux$`PD Response` <- relevel(d2ux$`PD Response`, ref="Attitude")
apa_lineplot(data=d2ux, id="cs", dv="Evaluative change", factors=c("PD Response","Valence memory response"), intercept=0, use = "all.obs", ylim=c(-4,4))
u2_ec_pd <- afex::mixed(data=subset(d2ux, Instruction=="Inclusion"), ec~Material*CS_Valence + pdset*vmval + (1|cs) + (CS_Valence|id), method="S", progress=FALSE)
p_pd <- print_mixedF(u2_ec_pd, "pdset:vmval")
#u2_ec.em <- emmeans(u2_ec, ~vmval|pdset)
u2_ec_pd.em <- emmeans(u2_ec_pd, ~pdset|vmval)
u2_ec_pd.c <- pairs(u2_ec_pd.em)



```

In support of this hypothesis, a significant contribution of valence memory to predicting CS evaluations was found, `r pq8`, that increased with subjective memory, `r pq9`.
In other words, the relation of valence-memory with evaluations became stronger with increasing confidence; this is illustrated in Figure \@ref(fig:u2b).
Interpreted as an influence of valence memory on evaluations, it suggests that participants increasingly relied on their (false) memory as their confidence in its accuracy grew.
Because we did not experimentally manipulate pre-post evaluative change for nonpaired stimuli, the causal direction of this phenomenon is unclear. 
Yet, as this finding parallels the above observation, for paired CSs, of an inverted EC effect for incorrect US valence responses that was restricted to high-confidence responses, we believe both effects may be related and reflect the same psychological mechanism.


### Pre-experimental valence informs memory responses

```{r}

## eq4: b41 & b42 sig; b43 ns
u_vm_m_eq4 <- afex::mixed(data=d2ux, vmpos~Material*Instruction + CS_Valence + Confidence + CS_Valence:Confidence + (1|cs) + (CS_Valence|id), method="S", progress=FALSE)
pq1 <- print_mixedF(u_vm_m_eq4, "CS_Valence")
pq2 <- print_mixedF(u_vm_m_eq4, "CS_Valence:Confidence")
## note: singular, random-ffcts correlations too high

```

Second, we explored the possibility that attitudinal information may be used to inform memory judgments.
Supporting this notion, our (pre-experimental) CS Valence manipulation affected valence-memory judgments, `r pq1`.
As a possible underlying process, consider the attitude-as-information heuristic: 
When uncertain, participants may rely on their (post-learning) CS evaluations to inform their memory responses [@stahl_respective_2009; @hutter_dissociating_2012].
This would suggest that the influence of evaluations on memory responses should be particularly prominent in lower-confidence cases, when memory is weak or absent.
However, contrary to this notion, the effect of CS Valence on valence-memory responses was unmodulated by Confidence, `r pq2`.
This finding, while consistent with the general notion that evaluations inform memory responses (e.g., by way of depending on a common representation), does not support an explanation by an attitude-as-information heuristic deployed under uncertainty.

