---
title: "R Notebook"
output:
  pdf_document:
    toc: yes
  html_document:
    fig_caption: yes
    keep_md: yes
    number_sections: yes
    toc: yes
editor_options:
  chunk_output_type: console
---

```{r setup_aer_0, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,cache=TRUE,message=FALSE,warning=FALSE)

library("papaja")
library(ggplot2)
library(lemon)
library(Matrix)
library(ggmosaic)

library(knitr)
library(afex)
options(contrasts=c('contr.sum', 'contr.poly'))
afex_options(check_contrasts=FALSE, method_mixed="S")

library(data.table)
library(lme4)
library(lmerTest)
library(tidyverse)
library(emmeans)


# load exp1 data

#d1 <- readr::read_delim("../modPD1/modPD1_clean.csv", ",", escape_double = FALSE, trim_ws = TRUE)
load(file="./data/modPD1_d1.RData")

d1p <- subset(d1, Pairing=="paired")
d1np <- subset(d1, Pairing=="nonpaired")
dx <- subset(d1np, pdset=="Attitude" & vm.resp!="dont know")

# load exp2 data

#d2 <- readr::read_delim("../modPD2/modPD2_d2.csv", ",", escape_double = FALSE, trim_ws = TRUE)
load(file="./data/modPD2_d2.RData")

## Exclude participants who failed the PD training test
d2 <- subset(d2, include==TRUE)
d2p <- subset(d2, US_Valence!="none")

```


## Relating EC and memory

The EC effect itself may also be better understood with the help of joint analyses of fine-grained memory measures. 
In line with the literature, EC effects in the present studies depended on objective US valence memory accuracy (see Appendix).
Here we extend the perspective by adding subjective memory indicators, first separately and then jointly with objective memory performance.
We focus on the evaluative ratings from Experiment 2, which allowed computing response-level EC effects for all levels of the subjective memory indicators.
First we describe how EC is related to subjective memory.
Next we characterize EC more fully by combining objective and subjective memory predictors.

### EC effects as a function of subjective memory

We used linear mixed models to account for EC effects (i.e., pre-post change in evaluative ratings) for paired CSs and how they are related to each of the three subjective memory indicators.
In the baseline model, EC was expressed as a function of the (fixed-effects) factors of the design (i.e., CS valence, US valence, CS material, PD instruction), with person and item random intercepts and slopes for US valence (crossed for persons and items) and CS valence (only for persons).
To this baseline model, one of the subjective-memory measures was then added as a covariate.
^[Adding random slopes for the subjective memory measures was prohibited because of model convergence problems. 
The Exclusion data were excluded from these analyses because of the potential distortion by carry-over effects. 
As a consequence, the PD Instruction factor was omitted from the analysis of PD Response as it had only a single level.]


```{r ec2-subj-sep}

d2px <- subset(d2p, Instruction!="Exclusion")

### base

ec2 <- afex::mixed(data=d2px, ecmag ~ CS_Valence*US_Valence*Material*Instruction + (US_Valence|cs) + (CS_Valence*US_Valence|id), method="S", progress=FALSE)


### EC by valmem accuracy

ec2_v_ <- afex::mixed(data=d2px, ecmag ~ CS_Valence*US_Valence*Material*Instruction + Valence_memory + (US_Valence|cs) + (CS_Valence*US_Valence|id), method="S", progress=FALSE)
ec2_v_.em <- emmeans(ec2_v_, ~Valence_memory) # zero for incorrect


### EC by idmem accuracy

d2px$Identity_memory <- factor(d2px$imcor)
ec2_i_ <- afex::mixed(data=d2px, ecmag ~ CS_Valence*US_Valence*Material*Instruction + Identity_memory + (US_Valence|cs) + (CS_Valence*US_Valence|id), method="S", progress=FALSE)
ec2_i_.em <- emmeans(ec2_i_, ~Identity_memory) # zero for incorrect


### EC by PD response
ec2_pd_I <- afex::mixed(data=subset(d2px, Instruction=="Inclusion"), ecmag ~ CS_Valence*US_Valence*Material + pdset + (US_Valence|cs) + (CS_Valence*US_Valence|id), method="S", progress=FALSE)
ec2_pd_I.em <- emmeans(ec2_pd_I, ~pdset) # M > a


### EC by Confidence

ec2_c_ <- afex::mixed(data=d2px, ecmag ~ CS_Valence*US_Valence*Material*Instruction + Confidence + (US_Valence|cs) + (CS_Valence*US_Valence|id), method="S", progress=FALSE)
ec2_c_.em <- emmeans(ec2_c_, ~Confidence) # l=m<h


### EC by RKG

ec2_r_ <- afex::mixed(data=d2px, ecmag ~ CS_Valence*US_Valence*Material*Instruction + RKG + (US_Valence|cs) + (CS_Valence*US_Valence|id), method="S", progress=FALSE)
ec2_r_.em <- emmeans(ec2_r_, ~RKG) # l=m<h

### print an F test from mixed
print_mixedF <- function(obj, term){
  if (!any(row.names(obj$anova_table)==term)) term <- paste0("`",term,"`")
  index <- which(row.names(obj$anova_table)==term)
  outF <- paste0("$F(", obj$anova_table[index,1], ",", round(obj$anova_table[index,2], 2), ")=", round(obj$anova_table[index,3],2))
  outp <- printp(obj$anova_table[index,4])
  out <- paste0(outF, ", p", ifelse(str_sub(outp,1,1)=="<", "", "="), outp, "$")
}


```

```{r}

p2 <- print_mixedF(ec2_v_, "Valence_memory")
p3 <- print_mixedF(ec2_i_, "Identity_memory")
p4 <- print_mixedF(ec2_pd_I, "pdset")
p5 <- print_mixedF(ec2_c_, "Confidence")
p6 <- print_mixedF(ec2_r_, "RKG")

```



EC was modulated by PD Response, `r p4`:
Effects were larger for Memory responses, `r apa_print(ec2_pd_I.em)$full_result$Memory`, and much smaller (and not significantly different from zero) for Attitude responses, `r apa_print(ec2_pd_I.em)$full_result$Attitude`.
Considerably weaker relations with EC were found for the confidence measure additionally collected in Experiment 2:
EC was related to participants' confidence in their US valence memory responses, `r p5`; but EC was present for the low, `r apa_print(ec2_c_.em)$full_result$low`, medium, `r apa_print(ec2_c_.em)$full_result$medium`, and high levels of confidence, `r apa_print(ec2_c_.em)$full_result$high`.
Finally, EC was related even less strongly to RKG level, `r p6` (and adding the RKG covariate to the model did not improve fit): 
It was present for the Guess, `r apa_print(ec2_r_.em)$full_result$G`, Know, `r apa_print(ec2_r_.em)$full_result$K`, and Remember responses, `r apa_print(ec2_r_.em)$full_result$R`.

```{r}

# Guess responses: how much confidence?
G_conf <- sum(prop.table(table(d2p$Confidence,d2p$RKG), margin = 2)[2:3,1])
# lowConf: how much K/R?
l_RKG <- sum(prop.table(table(d2p$Confidence,d2p$RKG), margin = 1)[1,2:3])

```


While the association of subjective-memory measures with EC differed in strength (with the strongest association for PD Response, where EC was largely absent from Attitude responses; and the weakest, and nonsignificant, association for RKG), EC was robust for the lowest levels of the Confidence and RKG indicators.
This finding of reliable EC for subsets of cases selected for their low subjective-memory level replicates recent research by @waroquier_distinguishing_2020, who also asked participants to attribute their US valence memory to one of several mnemonic states (Memory, Intuition, Random guessing, defined in a similar manner as in the present RKG task).
They found EC effects for all levels of their subjective memory measure, including 'Random guessing' attributions (analogous to the Guess state in the present study), suggesting that EC can occur in the absence of subjective memory for US valence.
They also found US valence memory for the Random guessing state to be at chance level---a finding we replicated (see previous section).
One possible interpretation of this pattern is that EC effects may arise in the absence of subjective and objective memory. 
However, this interpretation may be misleading due to operation of selection bias; in fact, in the present data, subjective memory was not entirely absent for the subsets of low-confidence or Guess responses:
There were substantial amounts of higher subjective-memory levels on the other measures (i.e., for paired CSs, in $`r printnum(G_conf*100,digits=1)`$% of Guess responses, participants reported medium or high confidence; and $`r printnum(l_RKG*100,digits=1)`$% of low-confidence responses were associated with Know or Remember attributions); furthermore, subjective memory was systematically related to objective memory (i.e., RKG predicted valence-memory accuracy among the subset of Attitude responses). 
These observations confirm previous research showing that subjective memory responses should not be interpreted at face value:
Participants stating that they have no memory may still have considerable (subjective and/or objective) memory that may be reflected in other (or repeated) measures.


### EC as a joint function of objective and subjective memory 

```{r ec-subjobj, fig.cap="EC by valence-memory accuracy and subjective memory (PD Response) for Experiment 1 (left) and Experiment 2 (right)."}


par(mfrow=c(1,2))

## Exp.1

d1_ <- subset(d1, Pairing=="paired")

d1_$`EC` <- d1_$ecmag
d1_$`Valence memory response` <- d1_$vm.resptype
apa_lineplot(data=d1_, id="Subject", dv="EC", factors=c("PD Response","Valence memory response"), intercept=0, use = "all.obs", ylim=c(-20,40)) 


ecmp1x <- afex::mixed(data=d1_, ecmag~typUS*Condition + vm.resptype*pdset + (typUS|Subject) + (typUS|ICS), method="S", progress=FALSE)

ecmp1 <- afex::mixed(data=d1_, ecmag~vm.resptype*typUS*pdset*Condition + (typUS|Subject) + (typUS|ICS), method="S", progress=FALSE)
ecmp1_ <- emmeans(ecmp1, ~vm.resptype|pdset)


## Exp.2

d2_ <- subset(d2, US_Valence!="none" & CS_Valence=="neutral" & Instruction!="Exclusion")
d2_$`EC` <- d2_$ecmag
d2_$`Valence memory accuracy` <- d2_$Valence_memory
papaja::apa_lineplot(data=d2_, id="id", dv="EC", factors=c("Confidence","Valence memory accuracy"), intercept=0, use = "all.obs", ylim=c(-2,4))

ecmp2 <- afex::mixed(data=d2_, ecmag~Material*Instruction*US_Valence + Valence_memory*Confidence + (US_Valence|cs) + (US_Valence|id), method="S", progress=FALSE)

ecmp2_ <- emmeans(ecmp2, ~Valence_memory)
ecmp2_ <- emmeans(ecmp2, ~Confidence|Valence_memory)
ecmp2_c <- pairs(ecmp2_)
hl1 <- apa_print(ecmp2_c)$full_result$`1_low_high`

```

One limitation of Waroquier et al's work is that they did not report joint analyses of both the objective and subjective variables they collected.
To explore the joint contribution of these variables, we predicted EC effects using linear mixed models with both objective and the subjective valence-memory indicators, as well as their interaction, as covariates.
We first considered the PD Response variable, which was collected in both experiments.
In Experiment 1, the EC effect was jointly modulated by valence-memory accuracy and PD Response, $F(2, 2754.95)=5.42, p=.004$:
Figure \@ref(fig:ec-subjobj) (left) shows that the lack of overall EC for Attitude responses was due to a mix of a regular EC for correct, an inversed EC for incorrect, and no EC for "don't know" responses [a frequent pattern; see for example @stahl_respective_2009].
Among Memory responses, EC emerged for "don't know" valence-memory responses, increased for correct responses, and was more strongly inverted for incorrect responses.


```{r}

### the RKG:valmem pattern

ec2a_r <- afex::mixed(data=subset(d2_), ecmag~Material*US_Valence*Instruction + Valence_memory*RKG + (US_Valence|cs) + (US_Valence|id), method="S", progress=FALSE)
p11 <- print_mixedF(ec2a_r, "Valence_memory:RKG")
ec2a_r.em <- emmeans(ec2a_r, ~RKG|Valence_memory)
ec2a_r.c <- pairs(ec2a_r.em)

## for G responses, still evidence for conscious EC?
ec2a_r <- afex::mixed(data=subset(d2_), ecmag~Material*US_Valence*Instruction + Valence_memory*Confidence*RKG + (US_Valence|cs) + (US_Valence|id), method="S", progress=FALSE)

ec2a_G <- afex::mixed(data=subset(d2_, RKG=="G" & Confidence !="high"), ecmag~Material*US_Valence*Instruction + Valence_memory*Confidence + (US_Valence|cs) + (US_Valence|id), method="S", progress=FALSE)
ec2a_R <- afex::mixed(data=subset(d2_, RKG=="R"), ecmag~Material*US_Valence*Instruction + Valence_memory*Confidence + (US_Valence|cs) + (US_Valence|id), method="S", progress=FALSE)
ec2a_K <- afex::mixed(data=subset(d2_, RKG=="K"), ecmag~Material*US_Valence*Instruction + Valence_memory*Confidence + (US_Valence|cs) + (US_Valence|id), method="S", progress=FALSE)

```


In Experiment 2, the Confidence measure was used to account for uncertainty, and a conceptually similar pattern emerged:
Figure \@ref(fig:ec-subjobj) (right) shows that (in addition to a main effect of valence-memory accuracy) EC was modulated by an accuracy-confidence interaction, $F(2, 1696.22)=  19.14, p <.0001$: 
With accurate memory, a regular EC effect emerged with low and increased with increasing confidence (only the high-low pairwise comparison was significant, `r hl1`). 
With inaccurate memory, the EC effect was more and more inverted with increasing confidence ($p<.05$ for all pairwise comparisons). 
An inverse EC effect was significant only for high-confidence responses, `r apa_print(ecmp2_)$full_result$high_0`.
^[A similar but weaker interaction pattern was found for the RKG responses, `r p11`: 
Robust inverse EC did not emerge for incorrect Remember responses, but results confirmed the dependence of EC on accurate memory even for low levels of subjective memory (here, Guess attributions).]



```{r waroquier, eval=FALSE}

par(mfrow=c(1,2))

# download from osf: https://osf.io/2g8se/download
# load data from excel
dw1 <- readxl::read_excel(path = "./data/Data_Waroquier et al._Conscious and unconscious knowledge in EC.xlsx", sheet = 1)
dw2 <- readxl::read_excel(path = "./data/Data_Waroquier et al._Conscious and unconscious knowledge in EC.xlsx", sheet = 2)

# reshape
dw1l <- pivot_longer(dw1, cols=Att_chang_PosCS_Overall_Corr_Id:Att_chang_NegCS_Random_Inc_Id
             , names_to=c("valence","Attribution","Accuracy")
             , names_pattern="Att_chang_(.*)CS_(.*)_(.*)_Id"
             , values_to = "Att_change")
dw1_ <- pivot_wider(dw1l, names_from = "valence", values_from="Att_change")
dw1_ <- subset(dw1_, Attribution !="Overall")

dw2l <- pivot_longer(dw2, cols=Att_chang_PosCS_Overall_Corr_Id:Att_chang_NegCS_Random_Inc_Id
             , names_to=c("valence","Attribution","Accuracy")
             , names_pattern="Att_chang_(.*)CS_(.*)_(.*)_Id"
             , values_to = "Att_change")
dw2_ <- pivot_wider(dw2l, names_from = "valence", values_from="Att_change")
dw2_ <- subset(dw2_, Attribution !="Overall")

dw2fl <- pivot_longer(dw2, cols=`Att_chang_PosCS_Overall_Corr_Id_Follow up`:`Att_chang_NegCS_Random_Inc_Id_Follow up`
             , names_to=c("valence","Attribution","Accuracy")
             , names_pattern="Att_chang_(.*)CS_(.*)_(.*)_Id_Follow up"
             , values_to = "Att_change")
dw2f_ <- pivot_wider(dw2fl, names_from = "valence", values_from="Att_change")
dw2f_ <- subset(dw2f_, Attribution !="Overall")

# compute EC
dw1_$EC <- dw1_$Pos - dw1_$Neg
dw2_$EC <- dw2_$Pos - dw2_$Neg
dw2f_$EC <- dw2f_$Pos - dw2f_$Neg

# define as ordered factor
dw1_$Attribution <- factor(dw1_$Attribution, ordered = TRUE, levels=c("Random", "Feeling", "Memory"))
dw2_$Attribution <- factor(dw2_$Attribution, ordered = TRUE, levels=c("Random", "Feeling", "Memory"))
dw2f_$Attribution <- factor(dw2f_$Attribution, ordered = TRUE, levels=c("Random", "Feeling", "Memory"))
#dw1_$`US Valence memory` <- factor(dw1_$`US Valence memory`, labels)

# analyze
#aov_ez(dw1_,  id="Subj_Number", dv="EC", within=c("Attribution","Accuracy")) # too many missings
dw1m <- afex::mixed(data=dw1_, EC ~ Accuracy*Attribution + (Attribution|Subj_Number), method="S", progress=FALSE)
dw1m.em <- emmeans(dw1m, ~Attribution|Accuracy)
dw1m.c <- pairs(dw1m.em)

# plot
papaja::apa_lineplot(dw1_, id="Subj_Number", dv="EC", factors=c("Attribution","Accuracy"), ylim=c(-60,60), intercept=0, args_legend=list(x="topleft"))
papaja::apa_lineplot(dw2_, id="Subj_Number", dv="EC", factors=c("Attribution","Accuracy"), ylim=c(-60,60), intercept=0, args_legend=list(plot=FALSE))
#papaja::apa_lineplot(dw2f_, id="Subj_Number", dv="EC", factors=c("Attribution","Accuracy"), ylim=c(-60,60), intercept=0, args_legend=list(plot=FALSE))

```


In sum, across both studies, the relation between EC and memory was illuminated when objective and subjective measures were considered jointly.
The regular EC effect (i.e., an evaluative change in the direction of the US's valence) depended on accurate (objective) valence memory even for low subjective-memory levels (Guess, Attitude or low-confidence responses).
The second half of the pattern (i.e., EC for incorrect valence memory responses) suggests that the inverse-EC phenomenon is not due to guessing under uncertainty, but based on subjectively convincing yet false experiences:
When participants had neither objective nor subjective memory of the US (i.e., "don't know", low-confidence, G responses), neither regular nor inverted EC was found; consistently across measures, an inverted EC effect was restricted to high-confidence false memories.
While our interpretation should be considered provisional and open to debate, the pattern itself is clearly reliable.
It is consistent not only across the present studies and with our own previous work, but also with novel independent data: 
The publicly available data from @waroquier_distinguishing_2020 allowed us to probe for a comparable pattern in their Experiment 1; the above interaction pattern replicated.


