---
title: "R Notebook"
output:
  html_document:
    fig_caption: yes
    keep_md: yes
    number_sections: yes
    toc: yes
  pdf_document:
    toc: yes
editor_options:
  chunk_output_type: console
---

This Appendix complements the more focused reporting of PD results in the main text by analyzing evaluative ratings and memory responses as a function of experimental factors. 
It also reports analyses of EC effects as a function of objective memory indicators.

```{r}

library(papaja)
library(afex)
library(emmeans)


#d1 <- read.csv(file="../modPD1/modPD1_clean.csv", ",", escape_double = FALSE, trim_ws = TRUE)
load(file="./data/modPD1_d1.RData")

d1p <- subset(d1, Pairing=="paired")
d1np <- subset(d1, Pairing=="nonpaired")
dx <- subset(d1np, pdset=="Attitude" & vm.resp!="dont know")

#d2 <- readr::read_delim("../modPD2/modPD2_d2.csv", ",", escape_double = FALSE, trim_ws = TRUE)
load(file="./data/modPD2_d2.RData")

## Exclude participants who failed the PD training test
d2 <- subset(d2, include==TRUE)

d2p <- subset(d2, US_Valence!="none")
d2np <- subset(d2, US_Valence=="none")

```

## Experiment 1

This section analyzes the (pre-post difference in) evaluative ratings, US valence memory, and US identity memory variables as a function of the factors of the 2 (PD Instruction) x 2 (Valence) x 2 (Pairing) design (with repeated measures on the last two factors).

### EC

EC was computed as post-learning evaluation minus pre-learning evaluation and submitted to a 2 (PD Instruction) x 2 (Valence) x 2 (Pairing) ANOVA with repeated measures on the last two factors.
Figure \@ref(fig:ec1appendix) and Table \@ref(tab:t1ec) show the results.

```{r ec1appendix, fig.cap="EC effects (pre-post evaluative changes) as a function of Valence, Pairing, and Condition."}

d1$`Evaluative change` <- d1$ec
apa_lineplot(data=d1, id="Subject", dv="Evaluative change", factors=c("Condition", "Valence","Pairing"), intercept=0, ylim=c(-25,25))
ec1 <- aov_ez(data=d1, id="Subject", dv="Evaluative change", within=c("Valence","Pairing"), between=c("Condition") )


```

EC was affected by Valence, Pairing, and their interaction:
For nonpaired CSs (left), pre-post changes reflected regression to the mean: 
The CSs with most extremely positive pre-ratings became less positive, and the CSs with most extremely negative pre-ratings became less negative.
For paired CSs (right), pre-post evaluative changes reflected US valence: 
Those paired with positive CSs became more positive while those paired with negative USs became more negative.

### Memory

```{r mem1dk, fig.cap="Valence memory 'dont know' responses as a function of Pairing, US Valence, and PD Condition."}

par(mfrow=c(1,2))

## proporiton of vm.dk 
d1$`Proportion dont know` <- d1$dk
vmdk1_ <- aov_ez(data=d1, id="Subject", dv="Proportion dont know", within=c("Valence","Pairing"), between=c("Condition") )

vmdk1 <- afex::mixed(data=d1, `Proportion dont know`~Pairing*Valence*Condition + (Valence|Subject) + (1|ICS), method="S", progress=FALSE)
## Pairing, Condition, Pairing:Condition, Valence:Condition
apa_barplot(data=d1, id="Subject", dv="Proportion dont know", factors=c("Condition", "Valence","Pairing"), intercept=.5, ylim=c(0,1), args_legend=list(x="topright"))
## --> Paired stimuli had lower dk rates
## --> Exclusion reduced the proportion of dk responses; especially for nonpaired stimuli (.8 -> .4), less so for paired (.4 -> .2)

vmcor1_  <- afex::mixed(data=d1, vmcor~Pairing*Valence*Condition + (Valence|Subject) + (1|ICS), method="S", progress=FALSE)
vmcor1p  <- afex::mixed(data=d1p, vmcor~Valence*Condition + (Valence|Subject) + (1|ICS), method="S", progress=FALSE) ## Valence only
vmcor1np <- afex::mixed(data=d1np, vmcor~Valence*Condition + (Valence|Subject) + (1|ICS), method="S", progress=FALSE) ## Condition, Valence:Condition
## --> Exclusion increases the proporiton of CS-valence-consistent responses for nonpaired stimuli
## --> this is stronger for negative than positive stimuli

## Pairing, Valence, Condition

#apa_lineplot(data=d1, id="Subject", dv="Valence memory accuracy", factors=c("Condition", "Valence","Pairing"), intercept=.5, ylim=c(0,1), args_legend=list(x="bottomright"))

#apa_lineplot(data=d1, id="Subject", dv="vm.pleasant", factors=c("Condition", "Valence", "Pairing"), intercept=.5, ylim=c(0,1), args_legend=list(x="bottomright"))

```

```{r mem1, fig.cap="Accuracy of memory for US Valence (left) and US identity (right) for paired CSs as a function of US Valence and PD Condition."}

par(mfrow=c(1,2))

d1p$`Valence memory accuracy` <- d1p$vmcor
d1p$`Identity memory accuracy` <- d1p$imcor
apa_lineplot(data=d1p, id="Subject", dv="Valence memory accuracy", factors=c("Condition", "Valence"), intercept=.5, ylim=c(.4,1), args_legend=list(plot=FALSE))
apa_lineplot(data=d1p, id="Subject", dv="Identity memory accuracy", factors=c("Condition", "Valence"), intercept=.5, ylim=c(.4,1))

vmcor1_m <- afex::mixed(data=d1p, vmcor~Valence*Condition + (Valence|Subject) + (1|ICS), method="S", progress=FALSE) ## Valence only
imcor1_m <- afex::mixed(data=d1p, imcor~Valence*Condition + (Valence|Subject) + (1|ICS), method="S", progress=FALSE) ## ns
vmcor1_a <- aov_ez(data=d1p, id="Subject", dv="vmcor", within=c("Valence"), between=c("Condition") )
imcor1_a <- aov_ez(data=d1p, id="Subject", dv="imcor", within=c("Valence"), between=c("Condition") )

```

```{r mem1np, fig.cap="Valence-memory responses (Proportion 'pleasant') for non-paired CSs by Valence, PD Condition, and PD Response (left: Memory; right: Attitude)."}

par(mfrow=c(1,2))

d1np$`Valence memory pleasant` <- d1np$vm.pleasant
apa_lineplot(data=subset(d1np, pdset=="Memory"), id="Subject", dv="Valence memory pleasant", factors=c("Condition", "Valence"), intercept=.5, ylim=c(0,1), args_legend=list(x="bottomright"))

apa_lineplot(data=subset(d1np, pdset=="Attitude"), id="Subject", dv="Valence memory pleasant", factors=c("Condition", "Valence"), intercept=.5, ylim=c(0,1), args_legend=list(x="bottomright"))

## all nonpaired stimuli: Valence, COndition, Valence:Condition (Valence effect stronger under Exclusion)
vmcor1np <- afex::mixed(data=d1np, vm.pleasant~Valence*Condition + (Valence|Subject) + (1|ICS), method="S", progress=FALSE)
#apa_lineplot(data=d1np, id="Subject", dv="vm.pleasant", factors=c("Condition",  "Valence"), intercept=.5)

# inclusion: F=29
vmcor1npi <- afex::mixed(data=subset(d1np, Condition=="Inclusion"), vm.pleasant~Valence + (Valence|Subject) + (1|ICS), method="S", progress=FALSE)
# exclusion: F=387
vmcor1npe <- afex::mixed(data=subset(d1np, Condition=="Exclusion"), vm.pleasant~Valence + (Valence|Subject) + (1|ICS), method="S", progress=FALSE)

# inclusion: valence
vmcor1npi <- afex::mixed(data=subset(d1np, Condition=="Inclusion"), vm.pleasant~Valence*pdset + (Valence+pdset|Subject) + (1|ICS), method="S", progress=FALSE)
# exclusion: valence, valence:pdset
vmcor1npe <- afex::mixed(data=subset(d1np, Condition=="Exclusion"), vm.pleasant~Valence*pdset + (Valence+pdset|Subject) + (1|ICS), method="S", progress=FALSE)


## only Memory Set
vmcor1np1 <- afex::mixed(data=subset(d1np, pdset=="Memory"), vmcor~Valence*Condition + (Valence|Subject) + (1|ICS), method="S", progress=FALSE) # no effects for Memory responses

## only Attitude Set
vmcor1np2 <- afex::mixed(data=subset(d1np, pdset=="Attitude"), vm.pleasant~Valence*Condition + (Valence|Subject) + (1|ICS), method="S", progress=FALSE) # strong effect of Condition, interacts with Valence

## --> Set1: no effect of PD Condition
## --> Set2: crosses over!
## Exclusion induces something that carries over to valmem responses (we can see it in nonpaired stimlui)


```

On the valence-memory task, participants indicated whether the given CS had been paired with pleasant or unpleasant USs, or whether they were uncertain about US valence ("don't know"). 
We first analyze the proportion of "don't know" responses; then, the remaining ("pleasant" or "unpleasant") responses were analyzed.


The proportion of "don't know" responses is depicted in Fig. \@ref(fig:mem1dk).
On average, participants indicated they "don't know" US valence in about one third of cases.
<!-- ***TODO: report ANOVA (table)***. -->
They tended to be more uncertain for nonpaired than paired stimuli; and under Inclusion than Exclusion instructions; the latter difference was particularly strong for nonpaired stimuli and weaker for paired stimuli.
(It was also stronger for negative than positive valence.)

Figure \@ref(fig:mem1) illustrates memory accuracy for paired CSs in Experiment 1.
US valence memory accuracy for paired CSs (left) was approximately 80%, with somewhat better memory for CSs paired with negative than positive USs, $F(1,103.92)=9.13, p=.003$ (and no effect of PD Condition).
US identity memory accuracy (right) was at chance (and was affected neither by US Valence nor PD Condition).

### EC and objective memory

This section analyzed how EC depends on objective memory accuracy.
Using paired CSs only, we analyzed EC in a 2 (PD Instruction) * 3 (US Valence Memory) * 2 (US Valence) mixed model with random person slopes for the US Valence factor.


```{r ec-mem-1, fig.cap="EC for neutral paired CSs in Experiment 1 (left) and Experiment 2 (right)."}

par(mfrow=c(1,2))

## Exp.1

d1_ <- subset(d1, Pairing=="paired")

d1_$`EC` <- d1_$ecmag
d1_$`Valence memory response` <- d1_$vm.resptype
apa_lineplot(data=d1_, id="Subject", dv="EC", factors=c("Valence memory response","Condition"), intercept=0, use = "all.obs", ylim=c(-20,20)) 

ecm1 <- afex::mixed(data=d1_, ecmag~vm.resptype*typUS*Condition + (typUS|Subject), method="S", progress=FALSE)

ecm1_ <- emmeans(ecm1, ~vm.resptype)
ecm1_typUS <- emmeans(ecm1, ~typUS)



## Exp.2

d2_ <- subset(d2, US_Valence!="none" & CS_Valence=="neutral")
d2_$`EC` <- d2_$ecmag
d2_$`Valence memory` <- d2_$Valence_memory
apa_lineplot(data=d2_, id="id", dv="ecmag", factors=c("Valence memory","Instruction"), intercept=0, use = "all.obs", ylim=c(-2,4)) 

ecm2 <- afex::mixed(data=d2_, ecmag~Valence_memory*US_Valence*Instruction + (US_Valence|id), method="S", progress=FALSE)

ecm2_ <- emmeans(ecm2, ~Valence_memory)
ecm2_c <- pairs(ecm2_)

```

EC effects in Experiment 1 were largely modulated by valence memory, $F(2, 2741.96)= 163.45, p  <.0001$:
In line with the literature, EC was found for cases with correct valence-memory responses, `r apa_print(ecm1_)$full_result$correct`; no EC was found for "don't know" responses, `r apa_print(ecm1_)$full_result$dontknow`; and an inverted EC effect was found for incorrect valence-memory responses, `r apa_print(ecm1_)$full_result$incorrect`.
^[An additional main effect of US Valence, $F(1, 164.58)=5.70, p=.02$, reflected slightly larger EC for positive than negative USs.]

At this point, we can conclude that the objective memory indicator of valence-memory accuracy strongly modulates the EC effect.



### Additional exploratory findings

Interestingly, for Attitude but not Memory responses, valence memory responses for non-paired CSs varied as a function of PD condition.
As Figure \@ref(fig:mem1np) (right) shows, valence-memory responses reflected pre-rated valence more strongly under Exclusion than under Inclusion; this was restricted to cases with Attitude responses.
This is evidence for a carry-over artifact from the PD task (perhaps similar to the one mentioned in the original PD article).


## Experiment 2

To complement the analyses of PD results in the main text, here we report analyses of evaluative ratings and the memory variables (US valence memory accuracy, confidence, and RKG responses; US identity memory accuracy) as a function of experimental factors (Instruction, Material, CS Valence, and US Valence). 

### EC

EC effects (i.e., post- minus pre-ratings) were entered into an ANOVA with all of the experimental factors (Table \@ref(tab:t2ec)).
Figure \@ref(fig:ec2) shows pre-post evaluative changes (PD Condition had no effect and is not depicted).

```{r ec2, fig.cap="EC as a function of Material, CS Valence, and US Valence"}

par(mfrow=c(1,2))

ec2 <- aov_ez(data=d2, id="id", dv="ec", within=c("CS_Valence","US_Valence"), between=c("Instruction","Material"))
d2$`US Valence` <- d2$US_Valence
d2$`CS Valence` <- d2$CS_Valence
d2$`Evaluative change` <- d2$ec
apa_lineplot(data=subset(d2), id="id", dv="Evaluative change", factors=c("CS Valence","US Valence","Material"), intercept=0, use = "all.obs", ylim=c(-6,6)) 


```

EC reflected strong regression to the mean for pre-experimentally valent CSs (i.e., CSs selected because they were initially most negative were later evaluated more positively; and vice versa).
EC also reflected US valence (pleasant USs increased liking, whereas unpleasant USs decreased it).
Both effects were stronger for toy figures than faces.
Interestingly, the US valence effect was not modified by CS valence: 
In contrast to the notion that EC works best for neutral CSs, the EC effect was of the same mangnitude for valent and neutral CSs.
However, one could argue that unfamiliar toy figures are more neutral than human faces, and so the larger EC effect for the toys could be taken to support that notion (which would need to be specified as referring to classes of materials, not individual CSs).
As another unexpected finding, the EC effect for faces was restricted to positive USs; there was no difference in EC between CSs paired with negative USs and those not paired at all (this was not the case for the toy figures).

### Memory

```{r valmem2, fig.cap="Valence memory responses (proportion 'pleasant'; left) as a function of CS Valence and US Valence; and US identity memory accuracy (right) by Material and PD Condition."}

par(mfrow=c(1,2))

## proportion "pleasant"

vmpos2 <- aov_ez(data=d2, id="id", dv="vmpos", within=c("CS_Valence","US_Valence"), between=c("Instruction","Material"))
d2$`Valence memory pleasant` <- d2$vmpos
apa_lineplot(data=d2, id="id", dv="vmpos", factors=c("CS Valence","US Valence"), intercept=.5, use = "all.obs", ylim=c(0,1), args_legend=list(x="bottomright")) 

## accuracy

vmpos2p <- aov_ez(data=d2p, id="id", dv="vmpos", within=c("CS_Valence","US_Valence"), between=c("Instruction","Material"))

## im

imcor2 <- aov_ez(data=d2p, id="id", dv="imcor", within=c("CS_Valence","US_Valence"), between=c("Instruction","Material"))
d2p$`Identity memory accuracy` <- d2p$imcor
apa_lineplot(data=d2p, id="id", dv="Identity memory accuracy", factors=c("Material","Instruction"), intercept=.5, use = "all.obs", ylim=c(0,1), args_legend=list(x="bottomright")) 


```

We first report US valence and US identity memory accuracy.
The proportion of "pleasant" responses on the valence memory item are given in Figure \@ref(fig:valmem2) (left).
As Table \@ref(tab:t2vm) shows, they mainly reflected both US valence and CS valence.
Smaller effects included a two-way interaction of these two factors, as well as interactions of Material with US Valence and CS Type.

Memory for US identity (Table \@ref(tab:t2im)) is shown in Figure \@ref(fig:valmem2), right panel.
Here, the strongest effect was of Material (better memory for faces than toys); much smaller were the interaction effects of Material with CS valence and with response format (the Material effect was reduced in the Inclusion group). 


```{r valmem2-conf, fig.cap="Valence memory confidence."}

par(mfrow=c(1,2))
d2$vmconf <- as.numeric(d2$Confidence)
vmconf2 <- aov_ez(data=d2, id="id", dv="vmconf", within=c("CS_Valence","US_Valence"), between=c("Instruction","Material"))

## paired

## Material, cstpe, mat:CS_Valence, usval
d2$`Valence memory confidence` <- d2$vmconf
apa_lineplot(data=d2, id="id", dv="Valence memory confidence", factors=c("CS Valence","US Valence","Material"), intercept=.5, use = "all.obs", ylim=c(1,3), args_legend=list(x="topright")) 

```


Next, we turned to the subjective confidence and remember/know/guess responses.
Valence-memory confidence (depicted in Fig. \@ref(fig:valmem2-conf)) varied as a function of US Valence (negative > positive > nonpaired) and CS Valence (valent > neutral).
The Material factor also affected confidence, and it entered interactions with US Valence and CS Valence (see Table  \@ref(tab:t2vmconf)).

<!-- #### Remember/Know/Guess -->

```{r rkg2, fig.cap="RKG as a function of CS Valence and US Valence"}

par(mfrow=c(1,2))

#valmem2 <- aov_ez(data=d2p, id="id", dv="vmcor", within=c("CS_Valence","US_Valence"), between=c("Instruction","Material"))
d2$Proportion.R <- as.numeric(d2$RKG == "R")
d2$Proportion.K <- as.numeric(d2$RKG == "K")
d2$Proportion.G <- as.numeric(d2$RKG == "G")
rkg.r <- aov_ez(data=subset(d2,US_Valence!="none"), id="id", dv="Proportion.R", within=c("CS_Valence","US_Valence"), between=c("Instruction","Material")) # usval, CS_Valence, mat:CS_Valence, mat
rkg.k <- aov_ez(data=subset(d2,US_Valence!="none"), id="id", dv="Proportion.K", within=c("CS_Valence","US_Valence"), between=c("Instruction","Material")) # no effects
rkg.g <- aov_ez(data=subset(d2,US_Valence!="none"), id="id", dv="Proportion.G", within=c("CS_Valence","US_Valence"), between=c("Instruction","Material")) # CS_Valence, usval, mat:CS_Valence
#apa_lineplot(data=d2, id="id", dv="Proportion.R", factors=c("CS_Valence","US_Valence","Material"), intercept=0, use = "all.obs", ylim=c(0,1)) 
#apa_lineplot(data=d2, id="id", dv="Proportion.G", factors=c("CS_Valence","US_Valence","Material"), intercept=0, use = "all.obs", ylim=c(0,1)) 

apa_lineplot(data=d2, id="id", dv="Proportion.R", factors=c("CS Valence","US Valence"), intercept=0, use = "all.obs", ylim=c(0,1)) 
#apa_lineplot(data=d2, id="id", dv="Proportion.K", factors=c("CS_Valence","US_Valence"), intercept=0, use = "all.obs", ylim=c(0,1)) 
apa_lineplot(data=d2, id="id", dv="Proportion.G", factors=c("CS Valence","US Valence"), intercept=0, use = "all.obs", ylim=c(0,1), args_legend=list(plot=FALSE)) 

```

R responses (Fig. \@ref(fig:rkg2), left panel) were more likely for paired (than nonpaired) CSs, for negative (than positive) USs, and for initially valent (than neutral) CSs (see Table \@ref(tab:t2rkg)).
In a mirror effect, G responses (Fig. \@ref(fig:rkg2), right panel) were less likely for paired CSs, negative USs, and initially valent CSs.
There were no effects of experimental factors on the proportion of K responses.
There were additional interactions with the Material factor (e.g., for toys, the valent-neutral effect was stronger for positive than negative CSs), but they did not change this overall pattern.

### EC and objective memory

```{r}
pam21 <- apa_print(ecm2_)$full_result$`1`
pam22 <- apa_print(ecm2_)$full_result$`0`
```

EC effects in Experiment 2 were also modulated by valence memory, $F(1, 1724.92)= 121.95, p  <.0001$:
Figure \@ref(fig:ec-mem-1) shows that EC was restricted to accurate,  `r pam21 `, and absent from inaccurate valence-memory responses,  `r pam22`.
The different pattern between studies can be attributed to the difference in valence-memory measures:
Experiment 1 allowed participants to refrain from responding (i.e., by selecting "don't know"), and the "incorrect" results therefore comprise only relatively rare high-confidence errors.
In Experiment 2, the "incorrect" category comprises both low- and high-confidence errors, thereby masking potential inverted EC effects (see also below).

### Additional exploratory findings

The carry-over artifact for nonpaired CSs, observed in Experiment 1 after Attitude responses under Exclusion instructions, was not replicated here.
It may have been disrupted by the change in response format between PD ("pleasant" vs. "unpleasant") and valence-memory task (confidence ratings).


## Tables

```{r t1ec}
apa_table( apa_print(ec1)$table, caption="EC effects in Experiment 1")
```

```{r t1vm_}
apa_table( apa_print(vmdk1_)$table, caption="Experiment 1, US valence memory uncertainty (proportion 'dont know')")
```

```{r t1cor_}
apa_table( apa_print(vmcor1_a)$table, caption="Experiment 1, US valence memory accuracy (proportion correct)")
```

```{r t1imcor_}
apa_table( apa_print(imcor1_a)$table, caption="Experiment 1, US identity memory accuracy (proportion correct)")
```




```{r t2ec}
apa_table( apa_print(ec2)$table, caption="EC effects in Experiment 2")
```

```{r t2vm}
apa_table( apa_print(vmpos2)$table, caption="Experiment 2: Valence memory responses (proportion 'pleasant')")
```

```{r t2im}
apa_table( apa_print(imcor2)$table, caption="Experiment 2: Identity memory accuracy")
```

```{r t2vmconf}
apa_table( apa_print(vmconf2)$table, caption="Experiment 2: Valence memory confidence (1=low, 3=high)")
```

```{r t2rkg}
apa_table( apa_print(rkg.r)$table, caption="Experiment 2: RKG responses (proportion 'remember')")
```


