---
output:
  pdf_document:
  html_document:
    fig_caption: yes
    keep_md: yes
editor_options:
  chunk_output_type: console
---

```{r setup2, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,cache=TRUE,message=FALSE,warning=FALSE)
options(scipen=1, digits=2)

library("papaja")
library(kableExtra)
library(stringr)
library(afex)
library(bfrr)
library(dplyr)
library(effectsize)
set_sum_contrasts()

#function to display results from Bayesian analyses conducted with the package bfrr
printBFRR <- function(bf, RR=TRUE){
  result = paste0(" $BF_{H1: ", bf$H1_model, "}=$ ", ifelse((bf$BF>999)|(bf$BF<.001), format(bf$BF, scientific=TRUE, bf$BF)))
  if(RR) result <- paste0(result, " (Robustness Region: ", bf$RR$sd[1], ", ", bf$RR$sd[2], ")" ) 
  #print(result) # use for debugging in the console
  result
}

# load data

load(file="./data/modPD2.RData")
d2 <- subset(d2, Instruction!="Exclusion")

## prepare variables

d2$ec <- d2$postrating - d2$prerating
d2$`US Valence` <- d2$US_Valence
d2$`CS Valence` <- d2$CS_Valence
d2$`Evaluative change` <- d2$ec

```


## Results

As in Experiment 1, we first report the results of a manipulation check (i.e., the effects of the experimental valence manipulations on evaluative ratings).
Next, we analyzed the responses on the TBS task.

### Evaluative conditioning

To probe for EC effects, pre-post evaluative changes were entered into an ANOVA with all of the experimental factors (Table \@ref(tab:t2ec)).
Figures \@ref(fig:ec2face) (face CSs) and \@ref(fig:ec2gogo) (toy CSs) illustrate pre-post evaluative change as a function of CS Valence and US valence.

```{r ec2face, fig.cap="Pre-post evaluative change as a function of CS Valence and US Valence (face CS material)"}

apa_beeplot(data=subset(d2, Material=="faces"), id="id", dv="Evaluative change", factors=c("CS Valence","US Valence"), intercept=0, use = "all.obs", ylim=c(-6,6)) 

```

```{r ec2gogo, fig.cap="Pre-post evaluative change as a function of CS Valence and US Valence (toy CS material)"}

apa_beeplot(data=subset(d2, Material=="gogos"), id="id", dv="Evaluative change", factors=c("CS Valence","US Valence"), intercept=0, use = "all.obs", ylim=c(-6,6)) 

```


```{r ec2}

ec2 <- aov_ez(data=d2, id="id", dv="ec", within=c("CS_Valence","US_Valence"), between=c("Instruction","Material"))

ec2p <- aov_ez(data=subset(d2, US_Valence!="negative"), id="id", dv="ec", within=c("CS_Valence","US_Valence"), between=c("Instruction","Material"))
## neutral-positive: F=64, p<.001, eta=.092, keine Interaktion mit Material
ec2pg <- aov_ez(data=subset(d2, US_Valence!="negative" & Material=="gogos"), id="id", dv="ec", within=c("CS_Valence","US_Valence"), between=c("Instruction"))
ec2pf <- aov_ez(data=subset(d2, US_Valence!="negative" & Material=="faces"), id="id", dv="ec", within=c("CS_Valence","US_Valence"), between=c("Instruction"))

ec2n <- aov_ez(data=subset(d2, US_Valence!="positive"), id="id", dv="ec", within=c("CS_Valence","US_Valence"), between=c("Instruction","Material"))
## neutral-negative: F=7, p=.01, eta=.009, Interaktion mit Material
ec2ng <- aov_ez(data=subset(d2, US_Valence!="positive" & Material=="gogos"), id="id", dv="ec", within=c("CS_Valence","US_Valence"), between=c("Instruction"))
ec2nf <- aov_ez(data=subset(d2, US_Valence!="positive" & Material=="faces"), id="id", dv="ec", within=c("CS_Valence","US_Valence"), between=c("Instruction"))

# EC for paired neutral CSs, M vs. A cases

d2MA <- subset(d2, Pairing=="paired" & CS_Valence=="neutral" & Instruction=="Inclusion")
ec2MA <- aov_ez(data=d2MA, id="id", dv="ec", within=c("US_Valence", "pdset"), between=c("Material"))
## usval***, pdset*, usval:pdset**
d2M <- subset(d2MA, pdset=="Memory")
ec2M <- aov_ez(data=d2M, id="id", dv="ec", within=c("US_Valence"), between=c("Material"))
#apa_beeplot(data=d2M, id="id", dv="ec", factors=c("Material","US_Valence"), intercept=0)
d2Mf <- subset(d2MA, pdset=="Memory" & Material=="faces")
d2Mg <- subset(d2MA, pdset=="Memory" & Material=="gogos")
#t.test(ec~US_Valence, data=d2Mf)
#t.test(ec~US_Valence, data=d2Mg)
d2A <- subset(d2MA, pdset=="Attitude")
ec2A <- aov_ez(data=d2A, id="id", dv="ec", within=c("US_Valence"), between=c("Material"))
#apa_beeplot(data=d2A, id="id", dv="ec", factors=c("Material","US_Valence"), intercept=0)
d2Af <- subset(d2MA, pdset=="Attitude" & Material=="faces")
d2Ag <- subset(d2MA, pdset=="Attitude" & Material=="gogos")
#t.test(ec~US_Valence, data=d2Af)
#t.test(ec~US_Valence, data=d2Ag)



```


We found robust US valence effects, `r apa_print(ec2)$full_result$US_Valence`.
Compared with nonpaired stimuli, pairing with pleasant USs clearly increased liking, `r apa_print(ec2p)$full_result$US_Valence`, whereas the reduction by unpleasant USs was considerably smaller,  `r apa_print(ec2n)$full_result$US_Valence`.

We also found a strong regression-to-the-mean artifact for pre-experimentally valent CSs (i.e., CSs selected because they were initially most negative were later evaluated more positively; and vice versa), `r apa_print(ec2)$full_result$CS_Valence`.
Interactions with Material indicated that both effects were stronger for toy figures than faces (CS Valence: `r apa_print(ec2)$full_result$Material_CS_Valence`; US Valence: `r apa_print(ec2)$full_result$Material_US_Valence`).
While the increase in liking was found for both materials (faces: `r apa_print(ec2pf)$full_result$US_Valence`, toys: `r apa_print(ec2pg)$full_result$US_Valence`), the reduction by unpleasant USs was limited to toy figures, `r apa_print(ec2ng)$full_result$US_Valence`, and absent from faces `r apa_print(ec2nf)$full_result$US_Valence`.
Interestingly, the US valence effect was not modified by CS valence, `r apa_print(ec2)$full_result$CS_Valence_US_Valence`: 
In contrast to the widespread notion that EC works best for neutral CSs, the EC effect was of the same magnitude for valent and neutral CSs.
^[It could be argued that unfamiliar toy figures are more neutral than human faces, and so the larger EC effect for the toys could be taken to support that notion, albeit applied to classes of materials varied between participants, not variations between CSs within participants.]
<!-- As another unexpected finding, the EC effect for faces was restricted to positive USs; there was no difference in evaluations between face CSs paired with negative USs and those not paired at all (this was not the case for the toy figures). -->

### Validation of the Two-button-sets procedure

The responses in the TBS task are given descriptively and in a condensed form in Table \@ref(tab:freqtable2), which is structured as in Exp. 1 for ease of reference by pairing status and valence (positive vs. negative; neutral foils are not shown, and data are collapsed across all other factors).

```{r freqtable2}

## frequencies

p <- with(subset(d2, Pairing=="paired"), table(pdset)) 
np <- with(subset(d2, Pairing=="nonpaired"), table(pdset)) 
p_ <- c(rep(paste0(p[1], " (", printp(p[1]/sum(p[1:2]),2),")"),2)
        , rep(paste0(p[2], " (", printp(p[2]/sum(p[1:2]),2),")"),2))
np_ <- c(rep(paste0(np[1], " (", printp(np[1]/sum(np[1:2]),2),")"),2)
        , rep(paste0(np[2], " (", printp(np[2]/sum(np[1:2]),2),")"),2))

p_ <- c(p[1], paste0(" (", printp(p[1]/sum(p[1:2]),2),")")
        , p[2], paste0(" (", printp(p[2]/sum(p[1:2]),2),")"))
np_ <- c(np[1], paste0(" (", printp(np[1]/sum(np[1:2]),2),")")
        , np[2], paste0(" (", printp(np[2]/sum(np[1:2]),2),")"))

ppos <- with(subset(d2, Pairing=="paired" & US_Valence=="positive"), table(pdset,pdval)) # pdresp: 1,3=pleas, 2,4=unpl
ppos_ <- c(ppos[1,2], ppos[1,1], ppos[2,2], ppos[2,1])

pneg <- with(subset(d2, Pairing=="paired" & US_Valence=="negative"), table(pdset,pdval)) # pdresp: 1,3=pleas, 2,4=unpl
pneg_ <- c(pneg[1,2], pneg[1,1], pneg[2,2], pneg[2,1])

nppos <- with(subset(d2, Pairing=="nonpaired" & CS_Valence=="positive"), table(pdset,pdval)) # pdresp: 1,3=pleas, 2,4=unpl
nppos_ <- c(nppos[1,2], nppos[1,1], nppos[2,2], nppos[2,1])

npneu <- with(subset(d2, Pairing=="nonpaired" & CS_Valence=="neutral"), table(pdset,pdval)) # pdresp: 1,3=pleas, 2,4=unpl
npneu_ <- c(npneu[1,2], npneu[1,1], npneu[2,2], npneu[2,1])

npneg <- with(subset(d2, Pairing=="nonpaired" & CS_Valence=="negative"), table(pdset,pdval)) # pdresp: 1,3=pleas, 2,4=unpl
npneg_ <- c(npneg[1,2], npneg[1,1], npneg[2,2], npneg[2,1])

ppos__ <- c( paste0(ppos_[1], " (", printp(ppos_[1]/sum(ppos_[1:2], pneg_[1:2]),digits = 2),")")
            ,paste0(ppos_[2], " (", printp(ppos_[2]/sum(ppos_[1:2], pneg_[1:2]),digits = 2),")")
            ,paste0(ppos_[3], " (", printp(ppos_[3]/sum(ppos_[3:4], pneg_[3:4]),digits = 2),")")
            ,paste0(ppos_[4], " (", printp(ppos_[4]/sum(ppos_[3:4], pneg_[3:4]),digits = 2),")"))

pneg__ <- c( paste0(pneg_[1], " (", printp(pneg_[1]/sum(ppos_[1:2], pneg_[1:2]),digits = 2),")")
            ,paste0(pneg_[2], " (", printp(pneg_[2]/sum(ppos_[1:2], pneg_[1:2]),digits = 2),")")
            ,paste0(pneg_[3], " (", printp(pneg_[3]/sum(ppos_[3:4], pneg_[3:4]),digits = 2),")")
            ,paste0(pneg_[4], " (", printp(pneg_[4]/sum(ppos_[3:4], pneg_[3:4]),digits = 2),")"))

nppos__ <- c(paste0(nppos_[1], " (", printp(nppos_[1]/sum(nppos_[1:2], npneg_[1:2]),digits = 2),")")
            ,paste0(nppos_[2], " (", printp(nppos_[2]/sum(nppos_[1:2], npneg_[1:2]),digits = 2),")")
            ,paste0(nppos_[3], " (", printp(nppos_[3]/sum(nppos_[3:4], npneg_[3:4]),digits = 2),")")
            ,paste0(nppos_[4], " (", printp(nppos_[4]/sum(nppos_[3:4], npneg_[3:4]),digits = 2),")"))

npneu__ <- c(paste0(npneu_[1], " (", printp(npneu_[1]/sum(npneu_[1:2], npneu_[1:2]),digits = 2),")")
            ,paste0(npneu_[2], " (", printp(npneu_[2]/sum(npneu_[1:2], npneu_[1:2]),digits = 2),")")
            ,paste0(npneu_[3], " (", printp(npneu_[3]/sum(npneu_[3:4], npneu_[3:4]),digits = 2),")")
            ,paste0(npneu_[4], " (", printp(npneu_[4]/sum(npneu_[3:4], npneu_[3:4]),digits = 2),")"))

npneg__ <- c(paste0(npneg_[1], " (", printp(npneg_[1]/sum(nppos_[1:2], npneg_[1:2]),digits = 2),")")
            ,paste0(npneg_[2], " (", printp(npneg_[2]/sum(nppos_[1:2], npneg_[1:2]),digits = 2),")")
            ,paste0(npneg_[3], " (", printp(npneg_[3]/sum(nppos_[3:4], npneg_[3:4]),digits = 2),")")
            ,paste0(npneg_[4], " (", printp(npneg_[4]/sum(nppos_[3:4], npneg_[3:4]),digits = 2),")"))

freqtable2 <- data.frame("M" = c(rep("M",2), rep("A",2))
                       , "CS"=p_ #c(rep(.64,2), rep(.36,2))
                       , "Foil"=np_ #c(rep(.08,2), rep(.92,2))
                       , "Val"=rep(c("+","-"),2)
                       , "CS.p"=ppos__ #c(ppos[1,1], ppos[1,2], ppos[2,3], ppos[2,4])
                       , "CS.n"=pneg__ #c(pneg[1,1], pneg[1,2], pneg[2,3], pneg[2,4])
                       , "Foil.p"=nppos__ #c(nppos[1,1], nppos[1,2], nppos[2,3], nppos[2,4])
                       #, "Foil.0"=npneu_ #c(nppos[1,1], nppos[1,2], nppos[2,3], nppos[2,4])
                       , "Foil.n"= npneg__ #c(npneg[1,1], npneg[1,2], npneg[2,3], npneg[2,4])
                  )

kbl(freqtable2, booktabs=TRUE, align="c", caption="Response frequencies (proportions) on the TBS task, separated by pairing status and valence but collapsed across all other factors (Exp 2). ") %>%
  kable_styling(latex_options = c("scale_down")) %>%
  collapse_rows(columns = 1, latex_hline = "major", valign = "middle")
# Chisq tests are reported for M responses to paired stimuli (memory accuracy), A responses to paired stimuli (EC without memory), M responses to nonpaired stimuli (attitude-consistent guessing), and A responses to nonpaired stimuli (pre-study attitudes).

print_chisq <- function(d){
  paste0("Chisq(",d$parameter,") = ", round(d$statistic,2), ", p = ", printp(d$p.value))
}


## chisq indep tests

memsubj_test2 <- chisq.test(matrix(c(p,np), nrow=2))
#memacc_test2 <- chisq.test(matrix(c(ppos[1,2:1], pneg[1,2:1]), nrow=2))
#attval_test2 <- chisq.test(matrix(c(nppos[2,2:1], npneg[2,2:1]), nrow=2))
#ec_wo_mem_test2 <- chisq.test(matrix(c(ppos[2,2:1], pneg[2,2:1]), nrow=2))
#consbias_test2 <- chisq.test(matrix(c(nppos[1,2:1], npneg[1,2:1]), nrow=2))

```


```{r exp2_logist}

# M/A judments

## all items

x2. <- glmer(pdset ~ Material*US_Valence*CS_Valence + (1 + CS_Valence + US_Valence|id), family = binomial, data=subset(d2), control=glmerControl(optimizer = "bobyqa"))

## unpaired only:
x2.u <- glmer(pdset ~ Material*CS_Valence + (1 + CS_Valence |id), family = binomial, data=subset(d2, Pairing=="nonpaired"), control=glmerControl(optimizer = "bobyqa"))

# paired only:
x2.p <- glmer(pdset ~ Material*US_Valence*CS_Valence + (1 + CS_Valence + US_Valence|id), family = binomial, data=subset(d2, Pairing=="paired"), control=glmerControl(optimizer = "bobyqa"))

# paired, by material:
x2.pf <- glmer(pdset ~ US_Valence*CS_Valence + (1 + CS_Valence + US_Valence|id), family = binomial, data=subset(d2, Pairing=="paired" & Material=="faces"), control=glmerControl(optimizer = "bobyqa"))

x2.pg <- glmer(pdset ~ US_Valence*CS_Valence + (1 + CS_Valence + US_Valence|id), family = binomial, data=subset(d2, Pairing=="paired" & Material=="gogos"), control=glmerControl(optimizer = "bobyqa"))



# pleas/unpleas judgments

## all items
d2$Proportion.pleasant <- d2$pdval == "positive"

x2 <- glmer(Proportion.pleasant ~ Material*US_Valence*CS_Valence*pdset + (1 + CS_Valence + US_Valence|id), family = binomial, data=subset(d2), control=glmerControl(optimizer = "bobyqa"))

## nonpaired foils --> csval-effect, not modulated by pdset

x2u <- glmer(Proportion.pleasant ~ Material*CS_Valence*pdset + (1 + CS_Valence|id), family = binomial, data=subset(d2, Pairing=="nonpaired"), control=glmerControl(optimizer = "bobyqa"))

## paired CSs - ***usval-effect modulated by pdset (larger in Mem, absent in Att)***; also csval effect was modulated (smaller in Mem, larger in Att)

x2p <- glmer(Proportion.pleasant ~ Material*US_Valence*CS_Valence*pdset + (1 + CS_Valence + US_Valence|id), family = binomial, data=subset(d2, Pairing=="paired"), control=glmerControl(optimizer = "bobyqa"))

## paired, separate by pdset

### top-left

x2pM <- glmer(Proportion.pleasant ~ Material*US_Valence*CS_Valence + (1 + CS_Valence + US_Valence|id), family = binomial, data=subset(d2, Pairing=="paired" & pdset=="Memory"), control=glmerControl(optimizer = "bobyqa"))

### bottom-left

x2pA <- glmer(Proportion.pleasant ~ Material*US_Valence*CS_Valence + (1 + CS_Valence + US_Valence|id), family = binomial, data=subset(d2, Pairing=="paired" & pdset=="Attitude"), control=glmerControl(optimizer = "bobyqa"))

## unpaired, separate by pdset

## bottom-right

x2uA <- glmer(Proportion.pleasant ~ Material*CS_Valence + (1 + CS_Valence|id), family = binomial, data=subset(d2, Pairing=="nonpaired" & pdset=="Attitude"), control=glmerControl(optimizer = "bobyqa"))

## top right

x2uM <- glmer(Proportion.pleasant ~ Material*CS_Valence + (1 + CS_Valence|id), family = binomial, data=subset(d2, Pairing=="nonpaired" & pdset=="Memory"), control=glmerControl(optimizer = "bobyqa"))

```

```{r tbs_correct_proportions_exp2, include=FALSE}
#keep only neutral paired CSs and participants that performed the TBS
dat_tbs = subset(d2, Pairing == "paired" & CS_Valence == "neutral" & !is.na(pdset)) %>% droplevels()

dat_tbs$pdset = as.factor(dat_tbs$pdset)

#for each participant, compute the proportion of correct identifications in the TBS
#meaning, say "positive" if the CS was paired with a positive US, and say "negative if the CS was paired with a negative US
dat_tbs$tbs_correct = as.factor(ifelse(dat_tbs$pdval == factor(dat_tbs$US_Valence, ordered = FALSE), "correct", "incorrect"))

prop_correct_tbs = dat_tbs %>% 
  group_by(id, tbs_correct, .drop=FALSE) %>% 
  summarise(n = n()) %>%
  mutate(freq = n / sum(n)) %>% group_by(id) %>% filter(!is.nan(freq))

colnames(prop_correct_tbs) = c("subject", "correct_response", "n_count", "prop")

#proportion correct only for memory buttons in the TBS
prop_correct_tbs_mem = dat_tbs %>% filter(pdset == "Memory") %>%
  group_by(id, tbs_correct, .drop=FALSE) %>% 
  summarise(n = n()) %>%
  mutate(freq = n / sum(n)) %>% group_by(id) %>% filter(!is.nan(freq))

colnames(prop_correct_tbs_mem) = c("subject", "correct_response", "n_count", "prop")

#tests
t_prop_correct_m = t.test(prop_correct_tbs_mem$prop[prop_correct_tbs_mem$correct_response=="correct"], mu = 0.5)
d_prop_correct_m = cohens_d(prop_correct_tbs_mem$prop[prop_correct_tbs_mem$correct_response=="correct"], mu = .5)

bf_prop_tbs_memory = bfrr(
  sample_mean = mean(prop_correct_tbs_mem$prop[prop_correct_tbs_mem$correct_response=="correct"])-.5, # mean of the sample
  sample_se = sd(prop_correct_tbs_mem$prop[prop_correct_tbs_mem$correct_response=="correct"])/sqrt(length(prop_correct_tbs_mem$prop[prop_correct_tbs_mem$correct_response=="correct"])), # SE of the sample
  sample_df = length(prop_correct_tbs_mem$prop[prop_correct_tbs_mem$correct_response=="correct"]) - 1, # degrees of freedom
  model = "normal",
  mean = 0, 
  sd = .15, 
  tail = 1, #one-tailed
  criterion = 3, 
  rr_interval = list( # ranges to vary H1 parameters for robustness regions
    sd = c(0, 2) 
  )
)
#summary(bf_prop_tbs_memory)

#proportion correct only for attitude buttons in the TBS
prop_correct_tbs_att = dat_tbs %>% filter(pdset == "Attitude") %>%
  group_by(id, tbs_correct, .drop=FALSE) %>% 
  summarise(n = n()) %>%
  mutate(freq = n / sum(n)) %>% group_by(id) %>% filter(!is.nan(freq))

colnames(prop_correct_tbs_att) = c("subject", "correct_response", "n_count", "prop")

#tests
t_prop_correct_a = t.test(prop_correct_tbs_att$prop[prop_correct_tbs_att$correct_response=="correct"], mu = 0.5)
d_prop_correct_a = cohens_d(prop_correct_tbs_att$prop[prop_correct_tbs_att$correct_response=="correct"], mu = .5)

bf_prop_tbs_att = bfrr(
  sample_mean = mean(prop_correct_tbs_att$prop[prop_correct_tbs_att$correct_response=="correct"])-.5, # mean of the sample
  sample_se = sd(prop_correct_tbs_att$prop[prop_correct_tbs_att$correct_response=="correct"])/sqrt(length(prop_correct_tbs_att$prop[prop_correct_tbs_att$correct_response=="correct"])), # SE of the sample
  sample_df = length(prop_correct_tbs_att$prop[prop_correct_tbs_att$correct_response=="correct"]) - 1, # degrees of freedom
  model = "normal",
  mean = 0, 
  sd = .15, 
  tail = 1, #one-tailed
  criterion = 3, 
  rr_interval = list( # ranges to vary H1 parameters for robustness regions
    sd = c(0, 10) 
  )
)
#summary(bf_prop_tbs_att)
```

We first investigated the effect of manipulated variables on the proportion of Memory-set responses.
We expected (and found) the memory manipulation to be reflected in a higher proportion of Memory-set responses for paired target CSs as compared to non-paired foil stimuli:
The majority of paired CSs (60%) were judged 'remembered' (i.e., received Memory-set responses); only a minority (15%) of nonpaired foils was also falsely 'remembered' as having been paired with a US.
^[In addition to confirming the effect of the memory manipulation, 
a logistic regression analysis (which included random intercepts as well as random slopes for US and CS Valence) of the choice of Response Set (Memory vs. Attitude), with CS Valence, US Valence, and Material as predictors, indicated effects of all three experimental factors.
We conducted separate analyses of paired CSs and nonpaired foils to simplify interpretation of these findings.
For paired CSs, effects of Material and CS Valence were found, as well as interactions of Material with both valence factors.
Valent CSs were more often judged 'remembered' than neutral CSs, `r apa_print(x2.p)$full_result$CS_Valence_Q`.
Faces were more often judged 'remembered' than toy figures, `r apa_print(x2.p)$full_result$Material1`. 
An additional Material x CS Valence interaction indicated that the 'Memory-set' advantage was observed for negative faces but positive toy figures, `r apa_print(x2.p)$full_result$Material1_CS_Valence_L`. 
Also, toy figures paired with negative (vs. positive) USs received 'Memory-set' responses somewhat more often, `r apa_print(x2.p)$full_result$Material1_US_Valence_L`. 
Neither Material (`r apa_print(x2.u)$full_result$Material1`) nor CS Valence (linear: `r apa_print(x2.u)$full_result$CS_Valence_L`, quadratic: `r apa_print(x2.u)$full_result$CS_Valence_Q`) affected judgments of nonpaired foils (and the US Valence factor has only a single level for these items).]



Next, we analyzed frequencies of "pleasant"/"unpleasant" responses for paired CSs as well as nonpaired foils. 
Overall, these judgments were affected by main effects of US Valence (`r apa_print(x2)$full_result$US_Valence_L`) and CS Valence (`r apa_print(x2)$full_result$CS_Valence_L`).
Importantly, the US Valence effect was again modulated by Response Set (i.e., it differed between Memory and Attitude-set responses, `r apa_print(x2)$full_result$US_Valence_L_pdset`). 
In addition, Response Set also interacted with CS Valence, with smaller CS Valence effects on Memory than Attitude judgments, `r apa_print(x2)$full_result$CS_Valence_L_pdset1`. 
^[Additional effects included a main effect of Response Set, `r apa_print(x2)$full_result$pdset`, a Response Set by Material interaction, `r apa_print(x2)$full_result$Material1_pdset1`.as well as three-way interactions of Response Set with CS Valence and Material,  `r apa_print(x2)$full_result$Material1_CS_Valence_Q_pdset1`, and with CS Valence and US Valence,  `r apa_print(x2)$full_result$US_Valence_L_CS_Valence_L_pdset1`.]
To break down these findings, we report separate analyses by item type (CSs vs. foils) and Response Set (Memory vs. Attitude), which jointly define the four quadrants of Table 2.

We focused first on paired CSs, for which "pleasant"/"unpleasant" responses for paired CSs showed the same pattern of effects as obtained in the overall analyses reported above.
Most importantly, the interaction of US Valence with Response Set (Memory vs. Attitude) was robustly significant, `r apa_print(x2p)$full_result$US_Valence_L_pdset`, suggesting that US Valence effect on judgments differed between Memory-set and Attitude-set responses.
For paired stimuli, Memory-set judgments (top left quadrant) quite accurately reflected actual US valence (albeit with a somewhat a lower accuracy than in Experiment 1):
When participants experienced remembering US valence for a paired stimulus, they were accurate in 70% of cases.
The strongest effect on Memory-set judgments was exerted by US Valence, `r  apa_print(x2pM)$full_result$US_Valence_L` (i.e., "pleasant" responses were more likely for CSs paired with pleasant USs). 
Additional (smaller) effects were obtained for CS Valence, `r  apa_print(x2pM)$full_result$CS_Valence_L` (with pleasant CSs more likely judged "pleasant", reflecting attitude-consistent guessing), and Material, `r  apa_print(x2pM)$full_result$Material` (with face CSs less likely to be judged "pleasant", perhaps reflecting the finding that pleasant face CSs were less likely classified using the 'Memory-set' responses).
^[In addition, the above three-way interaction between Response Set, Material, and CS Valence was reflected here as a significant Material by CS Valence interaction, `r apa_print(x2pM)$full_result$Material1_CS_Valence_Q`.]

### Is evaluative conditioning observed in the absence of conscious retrieval of the CS-US pairings?

Next, Attitude-set judgments for paired CSs were analyzed, with a particular focus on whether or not they are influenced by US valence in a similar manner as were Memory-set judgments.
However, as reflected in the bottom-left quadrant of Table 2, those CSs were not evaluated in accordance with US valence.
In a logistic regression, only a CS Valence effect on these judgments was found, `r  apa_print(x2pA)$full_result$CS_Valence_L` (with initially pleasant CSs more likely judged pleasant). 
Importantly, replicating the absence of an EC-without-memory effect, US Valence did not affect these judgments, `r  apa_print(x2pA)$full_result$US_Valence_L`.
<!-- (z=.13, p=.9). -->

As in Experiment 1, we additionally computed a BF on the proportions of responses in line with US Valence for paired neutral CSs that received an Attitude-set judgment.
Going beyond failing to find an EC effect for Attitude-set responses, the Bayesian analysis yielded evidence against above-chance responses in line with US valence (*M =* `r mean(prop_correct_tbs_att$prop[prop_correct_tbs_att$correct_response=="correct"])`; *SD =* `r sd(prop_correct_tbs_att$prop[prop_correct_tbs_att$correct_response=="correct"])`).
This supports the absence of an EC effect in the absence of experiences of remembering, `r printBFRR(bf_prop_tbs_att)`. ^[Note that this conclusion holds even for very small effects.]

### Is there evidence for an affect-as-information bias?

Pleasantness judgments of nonpaired foils (i.e., stimuli not presented together with USs) varied only as a function of pre-experimental valence, `r  apa_print(x2u)$full_result$CS_Valence_L`, and this effect was not modulated by Response set, `r  apa_print(x2u)$full_result$CS_Valence_L_pdset1`.
For those (relatively few) foils for which participants falsely 'remembered' that a US had been paired with them (i.e., used the Memory response set; top right quadrant), they reported a US valence on the novel task that tended to be consistent with pre-experimental attitudes: 
A stimulus falsely judged as having been paired with a US was evaluated in accordance with pre-existing attitudes in 72% of cases. 
However, note that in a logistic regression of this relatively small subset of responses, the effect of pre-existing valence (while descriptively consistent with the overall analysis) was not significant, `r  apa_print(x2uM)$full_result$CS_Valence_L`.

Focusing on the bottom right quadrant (i.e., Attitude-set judgments for nonpaired stimuli), it is apparent that judgments reflected pre-experimental attitudes, `r  apa_print(x2uA)$full_result$CS_Valence_L`:
Participants consistently reported the attitude corresponding to their pre-study ratings in 84% of cases; besides a strong effect of CS Valence, the logistic regression analysis did not yield other significant predictors.

In sum, responses on the TBS task again appropriately reflected the memory and attitude manipulations.
We replicated the absence of EC without memory (i.e., the effect of US Valence was limited to Memory-set responses).
We also replicated the attitude-as-information bias (i.e., the effect of CS Valence), which was now obtained not only for nonpaired foils but also for paired CSs.
